Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-01-14 WSSSPE4_report/WSSSPE4_report.tex
adding note about keynote summary potential authors
adding social science working group draft

\author{Daniel S.\ Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$,
Sandra Gesing$^{(3)}$,
Lorraine Hwang$^{(4)}$,
Alice Allen$^{(5)}$,
Neil Chue Hong$^{(6)}$,
Anshu Dubey$^{(7)}$,
Jonah Miller$^{(8)}$,
Jean Salac$^{(9)}$,
Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: ?}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: ?}
%
\thanks{{}$^{(5)}$ \note{info needed}}
%
\thanks{{}$^{(6)}$ \note{info needed}}
%
\thanks{{}$^{(7)}$ \note{info needed}}
%
\thanks{{}$^{(8)}$ \note{info needed}}
%
\thanks{{}$^{(9)}$ \note{info needed}}

@@

\note{need a person to write this}

>>>>

\author{Daniel S.\ Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$,
Sandra Gesing$^{(3)}$,
Lorraine Hwang$^{(4)}$,
Alice Allen$^{(5)}$,
Neil Chue Hong$^{(6)}$,
Anshu Dubey$^{(7)}$,
R. Stuart Geiger$^(8)$,
Jonah Miller$^{(9)}$,
Jean Salac$^{(10)}$,
Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: ?}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: ?}
%
\thanks{{}$^{(5)}$ \note{info needed}}
%
\thanks{{}$^{(6)}$ \note{info needed}}
%
\thanks{{}$^{(7)}$ \note{info needed}}
%
\thanks{{}$^{(8)}$ \note{info needed}}
%
\thanks{{}$^{(9)}$ \note{info needed}}
%
\thanks{{}$^{(10)}$ \note{info needed}}

@@

\note{need a person to write this - Dan has asked Patricia if she will, if not, perhaps Dan will do it}

### 2017-01-14 WSSSPE4_report/wg_social.tex
adding social science working group draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Letters of evaluation for computational scientists}
\label{sec:letters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\note{Wolfgang to write this}

Introduction to group here, including the overall objective of work in this area.

@@

members of the working group

@@

Specific things the working group wants to accomplish in the context of the larger objective.

@@

What is the gap or challenge being addressed?

@@

What people, groups, or resources are needed.

@@

What tasks will the working group undertake

@@

What are the first SMART steps proposed?

@@

How could a reader get more information or get more involved?

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Social science for scientific software}
\label{sec:social}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\note{Stuart to write this}

Introduction to group here, including the overall objective of work in this area. \todo{}

@@

Stuart Geiger <stuart@stuartgeiger.com>, Lorraine Hwang <ljhwang@ucdavis.edu>, Robert McDonald <rhmcdona@indiana.edu>

@@

To give social scientists and practitioners working on scientific software, software sustainability, and open source and a better understanding of each other's work, as well as help them connect and coordinate on specific projects of mutual interest.

@@

There is more and more academic research being done on topics related to software sustainability, including work on software engineering practices and management of open source projects. However, academic research in general is often siloed for many reasons, and work on topics relevant to software sustainability is no exception. There are many academic studies and projects which may be relevant for practitioners working in this area, and many projects and initiatives by practitioners that may be relevant for social scientists. However, there is a gap between these two research and practice. Furthermore, we also recognize that academic social science and research software engineering are not monolithic, and there is a need to connect people who care about research-driven best practices inside of these two domains with each other as well.

@@

People: a network of invested social scientists and research software engineers who care about research on software engineering practices
Resources: a mailing list and a central repository for collecting literature and documenting lessons learned

@@

What tasks will the working group undertake \todo{}

@@

\begin{itemize}
\item Collect research questions RSEs have for social scientists (done)
\item Create a mailing list for people interested in this topic (done) \url{https://groups.google.com/forum/#!forum/researchsoftwarestudies}
\item Create a central repository for collecting literature and documenting lessons learned
\item Publicize mailing list and collect (more) research questions/topics/literature/researchers
\item Write up synthesis document 
\end{itemize}

@@

Join the mailing list at \url{https://groups.google.com/forum/#!forum/researchsoftwarestudies}
